---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(lubridate)
```

## Loading and preprocessing the data

```{r}
data <- read_csv("activity.zip") %>%
  mutate(minute=((interval %/% 100) * 60 + interval %% 100))
```



## What is mean total number of steps taken per day?

```{r}
steps_per_day <- data %>%
  group_by(date) %>%
  summarize(steps=sum(steps, na.rm=TRUE))
ggplot(steps_per_day, aes(x=date, y=steps)) +
  geom_col() +
  xlab("Date") + ylab("Steps") + ggtitle("Mean steps per day")
```

The median steps per day taken is `r median(steps_per_day$steps)`, the mean steps per day taken are `r mean(steps_per_day$steps)`.


## What is the average daily activity pattern?

```{r}
steps_per_interval <- data %>%
  group_by(minute, interval) %>%
  summarize(steps=mean(steps, na.rm=TRUE))
ggplot(steps_per_interval, aes(x=minute, y=steps)) +
  geom_line() + 
  xlab("Minute of the day") + ylab("Steps") +
  ggtitle("Mean steps per 5-minute interval")
```

```{r}
max_interval <- (steps_per_interval %>%
  arrange(desc(steps)))[1,]
```

The `r max_interval$interval` contains the most steps.

## Imputing missing values

There are `r sum(is.na(data$steps))` rows with missing step values.




## Are there differences in activity patterns between weekdays and weekends?
